### 2022-01-18 src-latex/main-paper.tex
minor changes

% Comment 
% FIXME : delete before submission :)
\newcommand{\bertrand}[1]{\textcolor{violet}{Bertrand:~#1}}
\newcommand{\nathalie}[1]{\textcolor{purple}{Nathalie:~#1}}
\newcommand{\edwin}[1]{\textcolor{pink}{Edwin:~#1}}

@@

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
\thanks{This work was supported by the French National Research Agency:
Project SoDuCo, grant ANR-18-CE38-0013. ???FIXME need acknowledgments for directory sources???}}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{LISTE PROVISOIRE PAR ORDRE ALPHA\\
%
Nathalie Abadie\inst{1}\orcidID{0000-0001-8741-2398} \and
Edwin Carlinet\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Joseph Chazalon\inst{3}\orcidID{2222--3333-4444-5555} \and
Bertrand Duménieu\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{LASTIG, Univ. Gustave Eiffel, IGN-ENSG, F-94160 Saint-Mandé, France\\
\email{nathalie-f.abadie@ign.fr}\\
\url{https://www.umr-lastig.fr/nathalie-abadie/} \and
INST, CITY, COUNTRY\\
\email{example@example.com}\\
\url{https://www.example.com} \and
CRH-EHESS, Paris, France\\
\email{bertrand.dumenieu@ehess.fr}\\ \url{http://crh.ehess.fr/index.php?5206}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

>>>>

% Comment 
% FIXME : delete before submission :)
\newcommand{\bertrand}[1]{\textcolor{violet}{Bertrand:~#1}}
\newcommand{\nathalie}[1]{\textcolor{purple}{Nathalie:~#1}}
\newcommand{\edwin}[1]{\textcolor{pink}{Edwin:~#1}}
\newcommand{\joseph}[1]{\textcolor{red}{Joseph:~#1}}

@@

\begin{document}
%
\title{A Benchmark of Named Entity Recognition Approaches in Historical Documents\\
Application to 19$^{th}$ Century French Directories%
% FIXME "19$^{th}$-Century" with dash?
\thanks{This work was supported by the French National Research Agency:
Project SoDuCo, grant ANR-18-CE38-0013. ???FIXME need acknowledgments for directory sources???}}
%
\titlerunning{A Benchmark of NER Approaches in Historical Documents}
%
\author{%
Nathalie Abadie\inst{1}\orcidID{0000-0001-8741-2398} \and
Edwin Carlinet\inst{2}\orcidID{0000-0001-5737-5266} \and
Joseph Chazalon\inst{2}\orcidID{0000-0002-3757-074X} \and
Bertrand Duménieu\inst{3}\orcidID{0000-0002-2517-2058}\\
{\footnotesize \emph{all authors contributed equally}}%
}
%
\authorrunning{N. Abadie et al.}
%
\institute{%
% 1
LASTIG, Univ. Gustave Eiffel, IGN-ENSG, F-94160 Saint-Mandé, France\\
\email{nathalie-f.abadie@ign.fr}\\
\url{https://www.umr-lastig.fr/nathalie-abadie/} \and
% 2
EPITA Research \& Development Laboratory (LRDE), Le Kremlin-Bicêtre, France\\
\email{\{edwin.carlinet,joseph.chazalon\}@lrde.epita.fr}\\
\url{https://lrde.epita.fr} \and
% 3
CRH-EHESS, Paris, France\\
\email{bertrand.dumenieu@ehess.fr}\\
\url{http://crh.ehess.fr/index.php?5206}%
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
\input{parts/00-abstract.tex}
\keywords{Historical documents \and Natural Language Processing \and Named Entity Recognition \and OCR noise \and Annotation cost.}
\end{abstract}

### 2022-01-18 src-latex/parts/50-xp-setup.tex
minor changes

\subsubsection{OCR systems parameters}
\nathalie{Y a-t-il des précisions à ajouter sur la façon dont ont été utilisés les OCR? Ou bien ce sont les versions "sur étagère" qui ont servi?}
\begin{itemize}
    \item Tesseract 4
    \item Pero
\end{itemize}

>>>>

\subsubsection{OCR systems parameters}
\nathalie{Y a-t-il des précisions à ajouter sur la façon dont ont été utilisés les OCR? Ou bien ce sont les versions "sur étagère" qui ont servi?}
\joseph{Totalement sur l'étagère. On a normalisé un peu les données après, c'est tout.}
\begin{itemize}
    \item Tesseract 4.1.1 (newest version: 5, released Nov. 2021)
    \item Pero OCR version from git repo, master branch updated on Sep 15, 2021 % 8b20f29    
    \item other?  % kraken if times allows
\end{itemize}

Pero OCR uses ParseNet \joseph{TODO ref} as internal layout parser for line detection.
Pero OCR uses an LSTM engine \joseph{TODO check + ref} for text line recognition.
Pero OCR generally works very well, as long as the bounding boxes of the regions to recognize are not too tightly adjusted.
Trained on newspapers in European languages by its development team.
Can output results in Latin, Greek and Cyrillic scripts, as well as some commonly-used typographic symbols.

% PERO refs
% O Kodym, M Hradiš: Page Layout Analysis System for Unconstrained Historic Documents. ICDAR, 2021.
% M Kišš, K Beneš, M Hradiš: AT-ST: Self-Training Adaptation Strategy for OCR in Domains with Limited Transcriptions. ICDAR, 2021.
% J Kohút, M Hradiš: TS-Net: OCR Trained to Switch Between Text Transcription Styles. ICDAR, 2021.
